Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2013-12-13 ms.tex
CO reference, more text and clean-up

All \PLANCK~data products utilized throughout this work are drawn from the\PLANCK~2013 data release \citep{planck2013}. Specifically, we have made use of the
the 217 GHz, 353 GHz, 545 GHz and 857 GHz intensity maps. We use the 
versions of these maps which have been corrected for zodiacal light 
\citep[\texttt{R1.10\_nominal\_ZodiCorrected},][]{planckzodi}.

@@

To incorporate information about the dust emission on the Wien side of its 
spectrum, we make use of 100$\mu$m data. In particular, we use the SFD 
reprocessing of IRAS 100$\mu$m, which we will refer to as \verb|i100| (Schegel et al. 1998). \verb|i100| has angular resolution of $6.1'$. %list other
%important characteristics of i100 e.g. that it has been zodi-corrected
% and relies on dirbe on scales larger than ???

@@

\subsection{Correlation against HI}
The raw \PLANCK~maps we have downloaded show offsets relative to HI, in the
sense that the FIR emission does not go to zero when HI emission goes to
zero. Since HI correlates linearly with far-IR emission in the diffuse ISM, 
when the optical depth is low and molecular effects are negligible, we modeled
far IR emission as a constant times HI emission, plus some offset. We then
subtracted the best-fit offset such that

\subsection{Molecular Emission}
One advantage of the FIRAS data used by FDS99 was its many narrow bins in 
frequency, which allowed those frequency ranges contaminated by strong 
molecular line emission to be discarded from the analysis. Unfortunately, with 
the broad \PLANCK~and \IRAS~bandpasses we do not have such a luxury. This means
 that we cannot truly separate out the thermal continuum of dust emission we 
wish to study from the molecular line emission. The most prominent molecular 
line emission in the Planck bands of interest arises from CO lines in the XX, 
YY bands. We investigated the possibility of subtracting out CO emission based 
on the template of

@@

\section{Markov Chains}
As explained in $\S$\ref{sec:modeling}, the two free parameters in our 
per-pixel dust emission SED are the hot dust temperature $T_2$, which 
determinesthe shape of the SED, and the spectrum normalization. In practice,
the normalization is controlled via $I^{*}_{545}$, the amplitude of the SED
in MJy/sr at $\nu$ = 545 GHz. For each pixel, we run a Metropolis-Hastings 
Markov chain sampling the posterior probability as a function of the two parameters $T_2$ and $I^{*}_{545}$. To be clear, we are sampling the posterior
given by:

\begin{equation}
P(I^{*}_{545}, T_2) \propto \mathcal{L}(\{I_i\}|I^{*}_{545}, T_2)P(T_2)
\end{equation}

>>>>

All \PLANCK~data products utilized throughout this work are drawn from the 
\PLANCK~2013 data release \citep{planck2013}. Specifically, we have made use 
of the the 217 GHz, 353 GHz, 545 GHz and 857 GHz intensity maps. We use the 
versions of these maps which have been corrected for zodiacal light 
\citep[\texttt{R1.10\_nominal\_ZodiCorrected},][]{planckzodi}.

@@

To incorporate information about the dust emission on the Wien side of its 
spectrum, we make use of 100$\mu$m data. In particular, we use the SFD 
reprocessing of IRAS 100$\mu$m, which we will refer to as \verb|i100|. \verb|i100| has angular resolution of $6.1'$. %list other
%important characteristics of i100 e.g. that it has been zodi-corrected
% and relies on dirbe on scales larger than ???

@@

\subsection{Correlation versus HI}
The raw \PLANCK~maps we have downloaded show offsets relative to HI, in the
sense that the FIR emission does not go to zero when HI emission goes to
zero. Since HI correlates linearly with far-IR emission in the diffuse ISM, 
when the optical depth is low and molecular effects are negligible, we modeled
far IR emission as a constant times HI emission, plus some offset. We then
subtracted the best-fit offset such that

\subsection{Molecular Emission}
One advantage of the FIRAS data used by FDS99 was its many narrow bins in 
frequency, which allowed those frequency ranges contaminated by strong 
molecular line emission to be discarded from the analysis. Unfortunately, with 
the broad \PLANCK~and \IRAS~bandpasses we do not have such a luxury. This means
 that we cannot truly separate out the thermal continuum of dust emission we 
wish to study from the molecular line emission. The most prominent molecular 
line emission in the Planck bands of interest arises from CO lines in the XX, 
YY bands. We investigated the possibility of subtracting out CO emission based 
on the template of \cite{planckco}. However, we found that the CO emission
rarely amounted to more than XX\% of the total intensity, and following
the treatment of \cite{planckdust}, $\S$2.1, we do not attempt to remove CO
emission.

@@

\section{Markov Chains}
As explained in $\S$\ref{sec:modeling}, the two free parameters in our 
per-pixel dust emission SED are the hot dust temperature $T_2$, which 
determinesthe shape of the SED, and the spectrum normalization. In practice,
the normalization is controlled via $\tilde{I}_{545}$, the amplitude of the 
model SED in MJy/sr at $\nu$ = 545 GHz. For each pixel, we run a 
Metropolis-Hastings Markov chain sampling the posterior probability as a function of the two parameters $T_2$ and $\tilde{I}_{545}$. To be clear, we are sampling the posterior
given by:

\begin{equation}
P(\tilde{I}_{545}, T_2) \propto \mathcal{L}(\{I_i\}|\tilde{I}_{545}, T_2)P(T_2)
\end{equation}
